### 2019-09-04 manuscript/manuscript.tex

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), and negative covariances between dislike seasons (i.e. Spring
2010 and Fall 2011) when fluctuating selection is strong and acts genome-wide,
as the original study found. However, while we find temporal covariances that
are non-zero, we find only weak support for a seasonal fluctuating model
driving these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

@@

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure XXX) as
expected. We then re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B).

@@

While \textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy}, they do not construct a null distribution of
p-values as would be expected if fluctuating selection were not acting. Without
such a distribution, we do not have a statistical expectation for the number of
variants across the genome with frequency trajectories that spuriously fit the
pattern of seasonal fluctuating selection. We found that we can create this
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model. We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.

>>>>

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
\gc{which found} evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years \gc{{\it in Drosophila melanogaster}}. As described in \textcite{Buffalo2019-io},
we \gc{might} expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), and negative covariances between dislike seasons (i.e. Spring
2010 and Fall 2011) when fluctuating selection is strong and acts genome-wide,
as the original study found. However, while we find temporal covariances that
are non-zero, we find only weak support for a seasonal fluctuating model
driving these covariances. In Supplementary Figure \gc{XXX}, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

@@

%We were concerned that this might be due to a flaw in our methods. To address
%this concern, we first ensured that our
\gc{To establish that our } temporal-covariance matrix bias
correction was working \gc{correctly}. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure XXX) as
expected.

\gc{It is unclear how strong the fluctuations would have to be to
  generate a genome-wide average signal of fluctuating selection from
  temporal covariances. For example,there many loci could still show a
  signal of fluctuating selection, but their average signals could be
  overwhelmed by other signals of fluctuating selection. To
  investigate whether there was an genome-wide excess} of loci showing evidence
  of fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \gc{\textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy},\gc{the bionomial null model does not
  include random evolutionary variation in allele frequencies. }

@@

%Without
%such \gc{an evolutionary null} distribution, we do not have a statistical expectation for the number of
%variants across the genome with frequency trajectories that spuriously fit the
%pattern of seasonal fluctuating selection. We found that we can

\gc{To investigate whether there is a genome-wide evidence of an
  enrichment of fluctuating selection we created an
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model \gc{, as proposed by {\bf
    Machado ET AL)}.} We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.
\gc{ADD MORE HERE}

%\gc{Note that this analysis does not rule out the idea that prior
 % analyses detected {\emph
  %  some} loci showing a pattern of fluctuating selection. Indeed
  %\textcite{Bergland2014-ij} provided a number of analyses that
  %suggested that their loci might be enriched for {\bf XXX}. However,
  %this reanalysis suggests that we currently lack genome-wide evidence
%of many loci experiencing fluctuating selection in {\it in Drosophila
 % melanogaster}. }
